abxD01 Paper

### 2015-03-04 PAPER.Rmd
Adjust legend in sfig1

plot(diversity$invsimpson[diversity$expgroup=="control"], 
     diversity$nextDayCFU[diversity$expgroup=="control"], 
     pch=pch.top[1], col=colors.top[1], xlim=c(0, 20), ylim=c(0,10),  
     cex=1.5, yaxt="n",  xaxt="n", cex.lab=1,
     ylab=as.expression("Log " ~ italic("C. difficile") ~ " CFU/g feces"), xlab="Inverse Simpson Index")

axis(1, las=1, cex.axis=1, at=seq(0,20, by=2))
axis(2, las=1, cex.axis=1, at=seq(0,10, by=1))

@@

legend(16, 6, legend=legend.labels.top, pch=pch.top, col=colors.top,  pt.cex=1.5, cex=1, bty="n", y.intersp=1.5)

>>>>

plot(diversity$invsimpson[diversity$expgroup=="control"], 
     diversity$nextDayCFU[diversity$expgroup=="control"], 
     pch=pch.top[1], col=colors.top[1], xlim=c(0, 25), ylim=c(0,10),  
     cex=1.5, yaxt="n",  xaxt="n", cex.lab=1,
     ylab=as.expression("Log " ~ italic("C. difficile") ~ " CFU/g feces"), xlab="Inverse Simpson Index")

axis(1, las=1, cex.axis=1, at=seq(0,25, by=5))
axis(2, las=1, cex.axis=1, at=seq(0,10, by=1))

@@

cor<-signif(results[1,1],2)
legend("topright", inset=0.05, legend=legend.labels.top, pch=pch.top, col=colors.top,  pt.cex=1.5, cex=1, bty="n", y.intersp=1.5)
